% !TeX spellcheck = en_GB
\documentclass[flowWeaver.tex]{subfiles}
\begin{document}
	\begin{easylist}[itemize]
		\ListProperties(Style1=\color{NavyBlue})
		& Senior Member of Technical Staff @ Oracle (\textit{Feb 2022 - Present})
		&& Project - Renewable Dashboard and SaaS Usage Metrics, The SaaS Tools and Innovation (TINNO)
		&&& The Renewal Dashboard provides a simple rules-based prediction of the likelihood of a customer to renew a particular subscription/pillar using the usage data of Oracle's SaaS customers.
		&&& The dashboard helps Oracle's sales and business executives to make timely business decisions.
		&&& The huge volume of usage data of Oracle's customers is gathered, aggregated, computed for metrics, and reporting from multiple in-house systems through Usage Metrics Project.
		&& Responsibilities
		&&& Design and implementation of multiple micro-services from scratch handling large volumes of data and reporting at the back-end.
		&&& Involved in development of multiple reusable front-end components using React.
		&& Tech Stack
		&&& Java, Spring Boot, Spring Security, Spring Batch, Hibernate, Oracle, OAuth 2.0, React, Mockito, Docker, Jenkins, SonarQube, Oracle cloud infrastructure

		& Specialist Software Engineer @ Société Générale (\textit{Oct 2020 - Feb 2022})
		&& Project - Rate Calculation Batch and Deals Reclassification Batch Automation
		&&& Rate Calculation Batch dealt with processing of huge volume of loans and deposits for overnight calculation.
		&&& Deals Reclassification Batch Automation dealt with credit rating-based reclassification of Non-performing Assets.
		&& Responsibilities
		&&& Design of MVP of micro-services in collaboration with Technical Architects.
		&&& Involved in feature implementation of the requirements at back-end.
		&&& Worked on POCs demonstrating BDD involving non-technical team members including Project owner and Business Analysts.
		&& Tech Stack
		&&& Java 8, Spring Boot (Spring batch), Microservices, BDD and cucumber, TDD and Mockito, OAuth 2.0

		& Senior Software Developer @ HealthAsyst® (\textit{Apr 2015 - Apr 2018})
		&& Project - Focus Script’s Service Portal
		&&& Focus Script’s Service Portal dealt with pharmacy data management though a web application interface for its stakeholders to manage users, pharmaceutical pricing data and remittances.
		&& Responsibilities
		&&& Built the enterprise application from scratch using Spring boot and Angular JS.
		&&& Responsible for building crucial modules for the application such as security (authentication and authorization), common libraries.
		&&& Responsible for designing, developing, testing, deployment, and continuous improvement of the software.
		&&& Managed a team of 3, project priorities, deadlines, and deliverables.
		&&& Created a fully automated test framework, build and deployment process through Jenkins for UAT tests.
		&&& Ensured high quality of delivery by code reviews through GitHub and SonarQube and implemented various security mechanisms for web application in accordance with OWASP-top 10.
		&& Tech Stack
		&&& Java, Spring boot and Microservices, Hibernate, Angular JS, Maven, Docker

		& Software Engineer @ NTT DATA (\textit{Jan 2013 - Apr 2015})
		&& Project - McKesson's One Content Control Centre
		&&& One Content Control Centre implemented as a dashboard dealt with observability and management of multiple components deployed across multiple bare metal servers.
		&& Responsibilities
		&&& Design, development, and end to end ownership of web application for component management and monitoring of McKesson's 'One Content' set of software.
		&&& Worked on resolving high priority application security issues raised by Veracode Platform
		&& Tech Stack
		&&& Java 7, Spring, Ext JS, Tomcat, Maven
	\end{easylist}
\end{document}